implementation quality control

### 2018-03-02 analysis/analyses/4-method_characterisation/7_quality_control.Rmd
update qc

table <- map(c("latex", "html"), function(format) {
  table <- checks %>% 
    mutate(
      weight = cell_spec(
        weight %>% {pritt(invisible_grouper[[format]])}, # add an invisible grouping indicator
        format,
        background = spec_color(weight, end=0.9,option="A",direction=-1),
        escape=FALSE,
        color="white"
      )
    ) %>%
    mutate(
      references = map_chr(references, citation_format[[format]])
    ) %>% 
    select(aspect, weight, references, item, item_weight) %>% 
    rename_all(label_long) %>% 
    knitr::kable(format, escape=FALSE) %>% 
    kable_styling(bootstrap_options = "striped", latex_options = c("striped", "scale_down")) %>% 
    landscape() %>% 
    collapse_rows(1:3)
  # 
  # for (category in unique(checks$category)) {
  #   color <- qc_categories %>% filter(category == !!category) %>% pull(color)
  #   table <- table %>% 
  #     group_rows(
  #       label_long(category), 
  #       min(which(checks$category == category)), 
  #       max(which(checks$category == category)),
  #       label_row_css = pritt("background-color: {color}; color: #fff;")
  #   )
  # }

  table
}) %>% set_names(c("latex", "html"))

table %>% write_rds(figure_file("qc_checks.rds"))
```

>>>>

table <- map(c("latex", "html"), function(format) {
  table <- checks %>% 
    mutate(
      weight = cell_spec(
        weight %>% {pritt(invisible_grouper[[format]])}, # add an invisible grouping indicator
        format,
        color = spec_color(weight,option="viridis",direction=-1),
        escape=FALSE
      )
    ) %>%
    mutate(
      references = map_chr(references, citation_format[[format]])
    ) %>% 
    mutate(
      category = cell_spec(
        label_long(category),
        format,
        color = set_names(qc_categories$color, qc_categories$category)[category],
        escape=FALSE
      )
    ) %>% 
    select(category, aspect, weight, references, item, item_weight) %>% 
    rename_all(label_long) %>% 
    knitr::kable(format, escape=FALSE) %>% 
    kable_styling(bootstrap_options = "striped", latex_options = c("scale_down")) %>% 
    landscape() %>% 
    collapse_rows(1:4)

  # if (format == "html") {
  #   for (category in unique(checks$category)) {
  #     color <- qc_categories %>% filter(category == !!category) %>% pull(color)
  #     table <- table %>%
  #       group_rows(
  #         label_long(category),
  #         min(which(checks$category == category)),
  #         max(which(checks$category == category)),
  #         label_row_css = pritt("background-color: {color}; color: #fff;")
  #     )
  #   }
  # }

  table
}) %>% set_names(c("latex", "html"))
table
table %>% write_rds(figure_file("qc_checks.rds"))
```
